Fitting Synchrotron Models to Gamma Ray Burst data from INTEGRAL/SPI

### 2021-11-29 src/ms.tex
aa style

% Title
\title{asdfasf}

% Author list
\author{Björn Biltzinger, Jochen Greiner, J. Michael Burgess, Thomas Siegert}

% Abstract with filler text
\begin{abstract}
  In the last years it has been shown, that it is needed to fit physical models to Gamma-Ray Burst (GRB) data to get more insights into their emission mechanism. For the energy range between ~ 10 keV to ~ 10 MeV Fermi/GBM has been the main instrument.... In this paper we show how we can add INTEGRAL/SPI to this analysis. INTEGRAL/SPI covers a similar energy range like Fermi/GBM and has a very good energy resolution of 2.2 keV at 1.3 MeV. Therefore INTEGRAL/SPI is an ideal instrument to precisely measure the curvature of the spectrum. In this work we present PySPI, a new analysis software we developed to analyze GRB data from SPI, and apply it to the GRB 120711A. We show that the GBM and the SPI data of this GRB can be fitted with a physical synchrotron model and that combining both, reduces the allowed parameter space.

\end{abstract}

@@

The first step in the spectral fitting with OSA is to use only the photo peak response of the detectors. These responses depend on the source position

@@

\subsection{Model Checking}
\ref{PPC}
To check if the fit of a model is a good description of the measured data is a very complicated topic and highly debated in the statistics community. Measurements like reduced $\chi^{2}$ assume that all the probability distributions in the problem are described as normal distributions, which is definitely not the case here, as for example the measurement process is a Poisson process. Therefore we decided to use Posterior Predictive Checks (PPCs), which use the posterior of the fit as well as the measurement process to simulate new data.

>>>>

% Title
\title{Fitting Synchrotron Models to Gamma Ray Burst data from INTEGRAL/SPI}

% Author list
\author{Björn Biltzinger \inst{mpe}, Jochen Greiner \inst{mpe}, J. Michael Burgess \inst{mpe}, Thomas Siegert \inst{mpe}}
\institute{Max-Planck-Institut fur extraterrestrische Physik, Giessenbachstrasse 1, D-85748 Garching, Germany \label{mpe}}
\date{Received 18 December, 2019; accepted 22 May, 2020}
% Abstract with filler text
\abstract{
  In the last years it has been shown, that it is needed to fit physical models to Gamma-Ray Burst (GRB) data to get more insights into their emission mechanism. For the energy range between ~ 10 keV to ~ 10 MeV Fermi/GBM has been the main instrument.... In this paper we show how we can add INTEGRAL/SPI to this analysis. INTEGRAL/SPI covers a similar energy range like Fermi/GBM and has a very good energy resolution of 2.2 keV at 1.3 MeV. Therefore INTEGRAL/SPI is an ideal instrument to precisely measure the curvature of the spectrum. In this work we present PySPI, a new analysis software we developed to analyze GRB data from SPI, and apply it to the GRB 120711A. We show that the GBM and the SPI data of this GRB can be fitted with a physical synchrotron model and that combining both, reduces the allowed parameter space.
}

\keywords{ (stars:) gamma ray bursts -- methods: data analysis --
  methods: statistical}

\maketitle

@@

The first step in the spectral fitting with OSA is to use only the photo peak response of the detectors. These responses depend on the source position, as this defines the absorption by the mask. With these responses and the different measured data in the individual SPI detectors, taking into account

@@

\subsection{Model Checking}
\label{PPC}
To check if the fit of a model is a good description of the measured data is a very complicated topic and highly debated in the statistics community. Measurements like reduced $\chi^{2}$ assume that all the probability distributions in the problem are described as normal distributions, which is definitely not the case here, as for example the measurement process is a Poisson process. Therefore we decided to use Posterior Predictive Checks (PPCs), which use the posterior of the fit as well as the measurement process to simulate new data.
